\textsf{Are large language models superhuman chemists?}

### 2024-10-17 src/tex/appendix.tex
Update src/tex/appendix.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

The corpus of the questions in Chembench, as shown in \Cref{tab:chembench_corpus}, can be divided according to which topic they belong, or which type of knowledge is required in order to solve them correctly.

>>>>

The corpus of the questions in  \chembench, as shown in \Cref{tab:chembench_corpus}, can be divided according to which topic they belong to or which type of knowledge is required to solve them correctly.
